A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-01-28 paper.tex
4d N=4 (1,2)

\begin{prop}
Suppose $Q_t$ is the rank $(1,2)$ supercharge of \eqref{eq:4d412Hodgefamily}. The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(2)}_{\rm gauge}$ (see \eqref{eq:gaugeI1}, \eqref{eq:gaugeI2}) in terms of the fields of 4d $\cN=4$ super Yang--Mills theory are
\begin{align*}
I_{\gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varphi, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varphi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
&+\int\dvol\left(\frac{t}{2} (F_{1, 1} + [\phi, \nu], \psi^*) + t\Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + t\Lambda \dd_{A_{1, 0}}\nu \chi^* + \right) \\
I^{(2)}_{\gauge} (Q_t, Q_t) &= \int \dvol \left(-\frac{1}{4}(\chi^*)^2\right) \\
\end{align*}
\end{prop}

>>>>

\begin{prop}
Suppose $Q_t$ is the rank $(1,2)$ supercharge of \eqref{eq:4d412Hodgefamily}. The $\MU(2)$ decomposition of the functionals $I^{(1)}, I^{(2)}$ (see \eqref{eq:gaugeI1}, \eqref{eq:gaugeI2}) in terms of the fields of 4d $\cN=4$ super Yang--Mills theory are
\begin{align*}
I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varphi, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varphi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varphi^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
I^{(2)} (Q_t, Q_t) &= \int \dvol \left(-\frac{1}{4}(\chi^*)^2\right) \\
\end{align*}
\end{prop}
